Bifurcation or state tipping: assessing transition type in a model trophic cascade

### 2018-07-15 paper/paper.Rmd
re-render

---
title: "Bifurcation or state tipping: assessing transition type in a model trophic cascade"
author:
  - name: Ryan Batt
    affiliation: rb
  - name: Carl Boettiger
    email: cboettig@berkeley.edu
    affiliation: espm
    footnote: Corresponding Author
address:
  - code: espm
    address: "Department of Environmental Science, Policy, and Management, University of California, Berkeley, CA 94720"
  - code: rb
    address: "Rensselaer Polytechnic Institute, Department of Biological Sciences, Troy, NY 12309 USA; 2Rutgers University, Department of Ecology, Evolution, and Natural Resources, New Brunswick, NJ 08901 USA"

>>>>

---
title: "Bifurcation or state tipping: assessing transition type in a model trophic cascade"
author:
  - name: Ryan Batt
    affiliation: rb
  - name: Carl Boettiger
    email: cboettig@berkeley.edu
    affiliation: espm
    footnote: Corresponding Author
address:
  - code: espm
    address: "Department of Environmental Science, Policy, and Management, University of California, Berkeley, CA 94720"
  - code: rb
    address: "Rensselaer Polytechnic Institute, Department of Biological Sciences, Troy, NY 12309 USA; Rutgers University, Department of Ecology, Evolution, and Natural Resources, New Brunswick, NJ 08901 USA"
